The title

### 2024-10-18 05_Manuscript/manuscript.Rmd
updating efa analyses

@@

also do five

@@

efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML1 >= .30 & ML2 >= .30, "no", "no"
      )
    )
  )) %>% 
  mutate(question = rownames(.))
```

@@

efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML3 >= .30, "yes", "no"
        )
      )
    )
  ) %>% 
  mutate(question = rownames(.)) %>% 
  mutate(
    keep = ifelse(
          (ML1 >= .30 & ML2 >= .30) | 
            (ML1 >= .30 & ML3 >= .30) |
            (ML3 >= .30 & ML2 >= .30), "no", keep
          )
  )
```

@@

efa_loadings_3 <- as.data.frame(unclass(EFA_fit_3$loadings)) %>% 
  mutate(question = rownames(.)) %>% 
  rowwise() %>%
  mutate(keep = sum(c_across(-question) >= .30)) %>% 
  ungroup()

>>>>

questions <- import("../03_Data/questions.xlsx")
```

@@

@@

efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML1 >= .30 & ML2 >= .30, "no", "no"
      )
    )
  )) %>% 
  mutate(question = rownames(.)) %>% 
  left_join(questions,
            by = c("question" = "Question_Number")) %>% 
  arrange(desc(ML1)) %>% 
  export(., "results/2_factor.xlsx", row.names = F)
```

@@

efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML3 >= .30, "yes", "no"
        )
      )
    )
  ) %>% 
  mutate(question = rownames(.)) %>% 
  mutate(
    keep = ifelse(
          (ML1 >= .30 & ML2 >= .30) | 
            (ML1 >= .30 & ML3 >= .30) |
            (ML3 >= .30 & ML2 >= .30), "no", keep
          )
  ) %>% 
  left_join(questions,
            by = c("question" = "Question_Number")) %>% 
  arrange(desc(ML1)) %>% 
  export(., "results/3_factor.xlsx", row.names = F)
```

@@

efa_loadings_3 <- as.data.frame(unclass(EFA_fit_3$loadings)) %>% 
  mutate(question = rownames(.)) %>% 
  rowwise() %>%
  mutate(keep = sum(c_across(-question) >= .30)) %>% 
  ungroup() %>% 
  left_join(questions,
            by = c("question" = "Question_Number")) %>% 
  arrange(desc(ML1)) %>% 
  export(., "results/5_factor.xlsx", row.names = F)
